### 2020-09-14 LaTeX/sections/abstract.tex
front-end of paper

Abstract goes here

>>>>

In the early days of Ethereum, developers experimented with exchange services (for digital assets) that operated fully on the blockchain. However for performance reasons, this idea has been abandoned for years in favour of a hybrid model where some functionality is done on-chain (\eg loading accounts, order cancelation) and some functionality (\eg matching orders) is done off-chain. As blockchain performance continues to improve (both in research and in practice), it is an ideal time to revisit the idea of a fully on-chain exchange---which has a superior security threat model---to benchmark what is possible performance-wise. We design and optimize a call market exchange, \cm, on Ethereum, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block. We also explore numerous extensions for further improvements.
